### 2021-06-17 README.Rmd
changes for re-submission to CRAN

## Attribution

- For more information about SHAP values in general, you can visit the [SHAP github page](https://github.com/slundberg/shap)
- If you use `{mshap}`, please cite [this article](https://www.google.com/)

>>>>

## Citations

- For more information about SHAP values in general, you can visit the [SHAP github page](https://github.com/slundberg/shap)
- If you use `{mshap}`, please cite [*mSHAP: SHAP Values for Two-Part Models*](https://arxiv.org/abs/2106.08990)
